\chapter{Conclusion and Future Work}

\section{Conclusion}
This project was a big challenge, and I really learned a lot in this journey.
It made me even more excited about algorithmic trading and the application of data science for it.
I'm now eager to build better models, explore different assets and markets, and add new features into the backtesting framework as mentioned in the next section for "Future Work".
I'm more motivated than ever to push my limits, see what more I can achieve, and am very curious about the outcomes of the experiments.

\section{Further Work}
In the continued development of the backtesting framework, several enhancements and updates are planned:

\begin{itemize}
    \item Implementation of regression-based and deep learning-based backtesting strategies.
    \item Development of an assembler that leverages multiple strategies from diverse machine learning and deep learning paradigms such as regression and classification.
    \item Integration of deep reinforcement learning for advanced trading strategies.
    \item Consideration for automated portfolio management functionalities.
    \item Exploring the incorporation of Natural Language Understanding for sentiment analysis.
Potential data sources for this sentiment analysis include platforms like Twitter, Reddit, and other trading-relevant sources.
    \item Adding notifications about trades using a Telegram bot.
    \item Adding support for backtesting and trading stocks with the Interactive Brokers platform.
    \item Incorporating more optimization techniques.
    \item Configuration options for backtesting and deployment for both long-only and long-short strategies.
\end{itemize}

Adding these features will enhance the flexibility of the backtesting framework, making it more resilient, and accurate.
