\chapter{Project Structure}
\dirtree{%
.1 backtester.
.2 .gitignore.
.2 drafts.txt.
.2 README.md.
.2 tree.py.
.2 backtesting/.
.3 set\_project\_path.py.
.3 indicators/.
.4 backtester\_base.py.
.4 bb\_backtester.py.
.4 ema\_backtester.py.
.4 fibonacci\_backtester.py.
.4 macd\_backtester.py.
.4 rsi\_backtester.py.
.4 sma\_backtester.py.
.4 so\_backtester.py.
.3 iterative\_backtesting/.
.4 backtester.py.
.4 comb\_strategies.py.
.4 config\_test.py.
.4 iterative\_backtester\_base.py.
.4 runner.py.
.4 strategies.py.
.4 config/.
.5 backtester\_config.json.
.5 config.py.
.5 strategy\_config.json.
.3 ml\_backtesting/.
.4 ml\_backtester.py.
.4 ml\_base\_backtester.py.
.4 ml\_classification\_backtester.py.
.4 ml\_datamanager\_new.py.
.4 ml\_model\_evaluator.py.
.4 ml\_model\_trainer.py.
.4 ml\_regression\_backtester.py.
.4 tester.py.
.4 config/.
.5 classification\_config.json.
.5 models\_config.py.
.5 regression\_config.json.
.4 optimization/.
.5 model\_factory.py.
.5 optimizer.py.
.5 tester.py.
.5 opt\_config/.
.6 classification\_config.json.
.6 models\_config.py.
.6 regression\_config.json.
.3 vectorized\_backtesting/.
.4 backward\_tester.py.
.4 basis\_tester.py.
.4 forward\_tester.py.
.4 strategy\_functions.py.
.4 config/.
.5 backward\_config.json.
.5 backward\_config.py.
.5 forward\_config.json.
.5 forward\_config.py.
.5 forward\_config\_updater.py.
.4 ml\_strategies/.
.5 MlBacktesterBase.py.
.5 MlDataPreparer.py.
.2 deployment/.
.3 binance/.
.4 backup.py.
.4 client\_manager.py.
.4 config.json.
.4 config.py.
.4 report\_manager.py.
.4 strategies.py.
.4 trader.py.
.2 docs/.
.3 uml/.
.2 historical\_data/.
.2 requirements/.
.3 requirements.txt.
.2 utilities/.
.3 credentials.py.
.3 data\_plot\_ml.py.
.3 data\_split.py.
.3 logger.py.
.3 performance.py.
.3 report\_email.py.
.3 xrp\_model.sav.
.3 data\_utils/.
.4 data\_loader.py.
.4 data\_manager.py.
.4 data\_retriever.py.
.4 data\_retriever\_base.py.
.4 ml\_data\_manager.py.
.4 ml\_feature\_engineer.py.
.3 plot\_utils/.
.4 backtesting\_plotter.py.
.4 ml\_backtesting\_plotter.py.
.4 ml\_data\_plot.py.
}
